Release flow is a set of steps to perform to release upcoming version of software product.
Main aim of this document is to present simple and working model of software release
using Semantic versioning~\cite{SemanticVersioning}, \texttt{Azure pipelines}
and \texttt{Mainline} development~\cite{MainlineDevelopment}.
Mainline development is also known as GitHub flow.
Current document is motivated by Microsoft's
\textit{Adopt a GIT branching strategy} available at~\cite{AdoptGitStrategy}.
Below picture shows main idea of GitHub flow itself
\input{sections/github-flow-diagram}
\begin{itemize}
    \item \textbf{Master} -- branch that contains tested, validated and verified code, ready to be released and deployed to production.
    \item \textbf{Feature} -- branch that contains implementation of a new feature according to sprint plan.
    The \texttt{feature} branch is based onto \texttt{master}.
    \item \textbf{Bugfix} -- branch that contains non-critical bug fix.
    The \texttt{bugfix} branch is based onto \texttt{master}, and merged back to \texttt{master} after fix is done.
    \item \textbf{Release/v*} -- branch that contains upcoming release state of software product, serves to keep small changes
    and updates to \texttt{CHANGELOG} file.
    The \texttt{Release/v*} branch is based onto \texttt{master}.
    The \texttt{Release/v*} branch is considered to be long-living branch, it should not be deleted after code is deployed to production.
    After release is completed it is merged back to \texttt{master}.
    \item \textbf{Hotfix} -- branch that contains critical bug fix.
    It is used to patch production environment and must be released as quick as possible.
    The \texttt{hotfix} branch is based onto the latest released \texttt{Release/v*} branch.
    After hotfix is released it is merged back to its base \texttt{Release/v*} and Cherry-picked~\cite{CherryPick}
    by \texttt{master}.
\end{itemize}

\subsection{Release process}\label{subsec:release-process}
\input{sections/sub-release-process}

\subsection{Hotfix strategy}\label{subsec:hotfix-strategy}
\input{sections/sub-hotfix-strategy}
